---
title: "German Credit Data Exploration_2"
author: "Dr. Prashant Mishra"
date: "3/26/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Import the Clean data
======================================================
We already have a clean file "german_credit_full.csv" to import. 
```{r}
credit_dataset <- read.csv("german_credit_full.csv",stringsAsFactors = TRUE)
str(credit_dataset)
colnames(credit_dataset)
```

2. Explore Class vs Checking Account Status, Credit History and Employment Duration
===================================================================================

```{r}
library(gmodels)
CrossTable(credit_dataset$CheckingAccountStatus, credit_dataset$Class)
```



```{r}
library(ggplot2)
pl1 = ggplot(credit_dataset, aes(x = CheckingAccountStatus, fill = Class));
pl2 = pl1 + geom_bar()
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
pl3 = pl1 + geom_bar(position = "fill") + ylab("proportion")
pl3+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
Two points:

1. It seems people who have Checking Account but only get amount between 0-200 DM are more likely to be a bad loan profile. 
2. People who don't have a checking account might have account else where (other banks). 



```{r}
pl1 = ggplot(credit_dataset, aes(x = CheckingAccountStatus, fill = EmploymentDuration));
pl2 = pl1 + geom_bar()+facet_grid(~Class)
pl2+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
pl2 = pl1 + geom_bar(position = "fill") + ylab("proportion")+facet_grid(~Class)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
pl1 = ggplot(credit_dataset, aes(x = CheckingAccountStatus, fill = CreditHistory));
pl2 = pl1 + geom_bar()+facet_grid(~Class)
pl2+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
pl2 = pl1 + geom_bar(position = "fill") + ylab("proportion")+facet_grid(~Class)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


2. Explore Class vs Purpose, Personal and Property
======================================================

```{r}
CrossTable(credit_dataset$Purpose,credit_dataset$Class)
CrossTable(credit_dataset$Personal,credit_dataset$Class)
CrossTable(credit_dataset$Property,credit_dataset$Class)
```


```{r}
pl1 = ggplot(credit_dataset, aes(x = Purpose, fill = Class));
pl1 + geom_bar()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
pl1 + geom_bar(position = "fill") + ylab("proportion")+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
pl1 = ggplot(credit_dataset, aes(x = Purpose, fill = Personal));
pl2 = pl1 + geom_bar()+facet_grid(~Class)
pl2+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
pl2 = pl1 + geom_bar(position = "fill") +ylab("proportion")+facet_grid(~Class)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
pl1 = ggplot(credit_dataset, aes(x = Purpose, fill = Property));
pl2 = pl1 + geom_bar()+facet_grid(~Class)
pl2+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
pl2 = pl1 + geom_bar(position = "fill") + ylab("proportion")+facet_grid(~Class)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

1. New Car loan seems to be worse than used car loans and any other loan.

2. Property doesn't seem to play a huge role as a deciding factor.


```{r}
pl1 = ggplot(credit_dataset, aes(x = Purpose, y = Amount, color=Purpose));
pl2 = pl1 + geom_boxplot()+facet_grid(~Class)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
pl1 = ggplot(credit_dataset, aes(x = Personal, y = Amount, color=Personal));
pl2 = pl1 + geom_boxplot()+facet_grid(~Class)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
pl1 = ggplot(credit_dataset, aes(x = Job, y = Amount, color=Job));
pl2 = pl1 + geom_boxplot()+facet_wrap(~Class,ncol = 2)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
pl1 = ggplot(credit_dataset, aes(x = Housing, y = Amount, color=Class));
pl2 = pl1 + geom_boxplot()+facet_wrap(~Personal,ncol=2)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
pl1 = ggplot(credit_dataset, aes(x = Purpose, y = Duration, color=Class));
pl2 = pl1 + geom_boxplot()+facet_wrap(~Personal,ncol=2)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
pl1 = ggplot(credit_dataset, aes(x = Personal, y = Amount, color=Class));
pl2 = pl1 + geom_boxplot()+facet_wrap(~Purpose, ncol = 5)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

1. Used car data show that that Female.NotSingle tend to take higher loan for Used car, and are more likely bad loans. 
2. Unsual data for Others, we might need to get more data on that. 



```{r}
pl1 = ggplot(credit_dataset, aes(x = Personal, y = Amount, color=Class));
pl2 = pl1 + geom_boxplot()+facet_wrap(~Job,ncol=2)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
1. Male single, Unemployed and Unskilled--- high risk
2. Female Not Single --- Also high risk
3. Male Divored/Separated Unskilled Resident -- high risk


```{r}
pl1 = ggplot(credit_dataset, aes(x = Personal, y = Amount, color=Class));
pl2 = pl1 + geom_boxplot()+facet_wrap(~CheckingAccountStatus,ncol=2)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
pl1 = ggplot(credit_dataset, aes(x = Personal, y = Amount, color=Class));
pl2 = pl1 + geom_boxplot()+facet_wrap(~CreditHistory,ncol=3)
pl2 + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
Just some detective skill: We can see the outlier in NoCredit.AllPaid, Female.NotSingle. Some one from Highskilled, management or self employed category with checking account status between 0 to 200 took the loan for others category. 










